Short_note_captured_phenotype

### 2025-02-05 Manuscript_data_analyses.qmd
Last figure changes

plot(ggemmeans(model_BM_PHO, terms = "MESH_SIZE"), show_data = T, jitter = 2, dot_alpha = 0.2) +
  ggtitle("Predicted by-caught individual's body mass\nas a function of used mesh size") +
  labs(y = "Body mass (kg)", x = "Mesh size (mm)")  +
  scale_y_continuous(limits = c(75, 300)) +
  theme(text = element_text(size = 30))

>>>>

plot(ggemmeans(model_BM_PHO, terms = "MESH_SIZE"), show_data = T, jitter = 2, dot_alpha = 0.2) +
  ggtitle("Predicted by-caught individual's body mass\nas a function of used mesh size") +
  labs(y = "Body mass (kg)", x = "Mesh size (mm)")  +
  scale_x_continuous(limits = c(75, 300)) +
  theme(text = element_text(size = 30))
